%%%%%%%%%%%%%%%%%%%%%% Generalities %%%%%%%%%%%%%%%%%%5
\documentclass[11pt,fleqn]{article}
\usepackage[paper=a4paper]
  {geometry}

\pagestyle{plain}
\pagenumbering{arabic}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{notas}
\usepackage{tikz}
%%%%%%%%%%%%%%%%%%%%%%%%%%% The usual stuff%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\NN{\mathbb N}
\newcommand\CC{\mathbb C}
\newcommand\QQ{\mathbb Q}
\newcommand\RR{\mathbb R}
\newcommand\ZZ{\mathbb Z}
\renewcommand\k{\Bbbk}

\newcommand\F{\mathcal F}
\newcommand\V{\mathcal V}
\newcommand\D{\mathcal D}
\renewcommand\H{\mathcal H}

\newcommand\maps{\longmapsto}
\newcommand\ot{\otimes}
\renewcommand\to{\longrightarrow}
\renewcommand\phi{\varphi}
\newcommand\Id{\mathsf{Id}}
\newcommand\im{\mathsf{im}}
\newcommand\coker{\mathsf{coker}}
%%%%%%%%%%%%%%%%%%%%%%%%% Specific notation %%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\g{\mathfrak g}
\newcommand\gl{\mathfrak{gl}}
\newcommand\gen{\mathsf{gen}}
\newcommand\std{\mathsf{std}}

\DeclareMathOperator\End{End}
\DeclareMathOperator\Sym{Sym}
\DeclareMathOperator\Alt{Alt}
\DeclareMathOperator\sg{sg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Singular Gelfand Tsetlin modules over $\gl$ à la Zadunaisky}
\date{[singular-GT.tex]}
\author{Pablo Zadunaisky}
\begin{document}
\maketitle

The objective of these notes is to understand the construction of Singular
Gelfand-Tsetlin modules due to Futorny, Grantcharov and Ramirez found in 
\cite{FGR}. 

\section{GT Tableaux and GT algebras}
References for all results can be found in \cite{FGR}*{section 3}.

\paragraph
Fix $n \in \NN_{\geq 2}$, and set $N = \frac{n(n+1)}{2}$. For each $m \in \NN$ 
set $U_m = U(\gl(m, \CC))$ and $Z_m \subset U_m$ its center, and set $U = 
U_n$. We get a chain of inclusions $U_1 \subset U_2 \subset \cdots \subset U_n$
induced by the maps sending standard generators $E_{i,j} \in \gl(k,\CC)$ to 
the corresponding $E_{i,j} \in \gl(k+1, \CC)$. 

\paragraph
\label{HC-morphism}
For each $m \in \NN$ the algebra $Z_m$ is a polynomial algebra on the 
generators
\[
	c_{m,k} = \sum_{(i_1, \ldots, i_k) \in [m]^k} E_{i_1,i_2} E_{i_2,i_3} 
		\cdots E_{i_k, i_1} \qquad \qquad 1 \leq k \leq m.
\]
Let $\Lambda_m = \CC[\lambda_{m,k} \mid 1 \leq k \leq m]$ be a polynomial
algebra in $m$ variables, and set
\[
	\gamma_{m,k} = \sum_{i = 1}^m (\lambda_{m,i}+m-1)^k 
	\prod_{i \neq j} \left( 1 - \frac{1}{\lambda_{m,i} - \lambda_{m,j}}\right).
\]
Although it is not obvious, the $\gamma_{m,k}$ are algebraically independent 
polynomials and they are invariant by the obvious action of the symmetric 
group $S_m$ on $\Lambda$; in fact $\Lambda_m^{S_m} = \CC[\gamma_{m,k} \mid 
1 \leq k \leq m]$, and there is an embedding $Z_m \to \Lambda$ given by 
$c_{m,k} \mapsto \gamma_{m,k}$. 

\paragraph
\label{GT-algebra}
We write $\Gamma = \CC[c_{m,k} \mid 1 \leq k \leq m \leq n] = 
\subset U$, which is the algebra generated by $\bigcup_{k=1}^n Z_k$. The 
$c_{m,k}$ are algebraically independent and hence this is isomorphic to a 
polynomial algebra in $N$ generators.

Let $\Lambda = \CC[\lambda_{i,j} \mid 1 \leq i \leq j \leq n]$ be a polynomial
algebra in $N$ variables. The group $S_m$ acts on $\Lambda$ 
permuting the variables $\lambda_{m,k}$ with $1 \leq k \leq m$ and fixing the 
rest. This induces an action of the group $G = S_n \times S_{n-1} \times 
\cdots \times S_1$ on $\Lambda$. Composing with the embedding from 
\ref{HC-morphism} we get that $\Gamma$ is isomorphic to $\Lambda^G$.

\note{I suppose this is just the Harish-Chandra morphism of each $Z_k$ pasted
together. Actually, is there \emph{a} HC morphism? In any case restriction to 
$Z_k$ gives an isomorphism with invariants in a polynomial algebra.}

\paragraph
\label{GT-tableaux}
Recall we have fixed $n \in \NN$ and set $N = \frac{n(n+1)}{2}$. A 
\newterm{Gelfand-Tsetlin 
tableau} of size $n$ is a vector $v \in \CC^{N}$, whose coordinates are 
indexed by $\{(i,j) \mid 1 \leq i \leq j \leq n\}$. We can represent this 
graphically as [INSERT IMAGE]. For ease of reference we will sometimes write 
\[
v = (v_{n,1}, v_{n,2}, \ldots v_{n,n} 
	\mid v_{n-1,1}, \ldots, v_{n-1,n-1} 
	\mid \cdots 
	\mid v_{1,1}).
\]

\paragraph
\label{various-tableau}
We say that a GT-tableau $v$ is 
\begin{itemize}
\item \newterm{integral} if $v \in \ZZ^{N}$. 

\item \newterm{standard} if for all $1 \leq i < j \leq k < n$ the difference 
$v_{k,i}-v_{k-1,i} \in \ZZ_{\geq 0}$ and $v_{k-1,i}-v_{k,i+1} \in \ZZ_{>0}$; 
we denote the set of standard tableaux by $\CC^N_\std$.

\item \newterm{generic} if for all $1 \leq i < j \leq k 
< n$ the difference $v_{k,i}-v_{k,j}$ is not in $\ZZ$; we denote the set of 
generic tableaux by $\CC^N_\gen$. 

\item \newterm{singular} if it is non-generic tableau, i.e. there is a pair of 
entries in the same line differing by an integer. If there is exactly one 
such pair then the tableau is called \newterm{1-singular}. Finally if two 
entries in the same row are equal the tableau is called \newterm{critical}.
\end{itemize}

\paragraph
Set $\ZZ^N_0 = \{v \in \ZZ^N \mid v_{n,i} = 0 \mbox{ for } 1 \leq i \leq n\}$.
For any ring $A$ we denote by $V_A$ the free $A$-module generated by all 
tableaux of the form $T(v)$ with $v \in \ZZ_0^N$. The group $G = S_n \times 
S_{n-1} \times \cdots \times S_1$ acts on $V_A$ in an obvious fashion.


\section{GT-modules}

\paragraph
\label{GT-formulas}
Set for each $1 \leq i \leq k \leq n$
\begin{align*}
p_{k,i}^\pm(\lambda) 
	&= \prod_{j = 1}^{k\pm1}(\lambda_{k,i} -\lambda_{k\pm1,j}); &
q_{k,i}(\lambda)
	&= \prod_{j \neq i} (\lambda_{k,i} - \lambda_{k,j}). \\
|\lambda|_k &= \lambda_{k,1} + \lambda_{k,2} + \cdots \lambda_{k,k}.
\end{align*}
Notice that $p_{k,i}^\pm(v)$ depends only on the $k, k \pm 1$-th rows of 
$v \in \CC^N$, while $q_{k,i}(v)$ depends only on the $k$-th row.

\paragraph
If $w$ is a GT tableau set 
\[
V(w) = \langle T(w+z) \mid z \in \ZZ^N_0 \rangle_\CC.
\]
The $T$ is just a symbol to remind us that we have a basis indexed by 
tableaux; in particular $T(v+z) \neq T(v) + T(z)$.

The following is a classical theorem which we quote without proof.
\begin{Theorem}[Gelfand-Tsetlin, '50]
\label{GT}
Let $\lambda = (\lambda_1, \ldots, \lambda_n)$ be a dominant weight of 
$\gl(n,\CC)$, and let 
\begin{align*}
V(\lambda) 
	&= \langle T(v) \mid v \in \CC^N_{\std} 
		\mbox{ and } v_{n,1} = \lambda_1, v_{n,2} = \lambda_2 - 1, \ldots, 
		v_{n,n} = \lambda_{n} - n +1
	\rangle_\CC
\end{align*}
(by convention, if $v$ is non-standard then $T(v) = 0$ in $V(\lambda)$).
Then
\begin{enumerate}[(a)]
\item \label{GT-structure}
$V(\lambda)$ is a $U$-module with the action of the canonical generators 
given by
\begin{align*}
E_{k,k+1} T(v) 
	&= - \sum_{i=1}^k \frac{p^+_{k,i}(v)}{q_{k,i}(v)} T(v + \delta^{k,i}) \\
E_{k+1,k} T(v) 
	&= \sum_{i=1}^k \frac{p^-_{k,i}(v)}{q_{k,i}(v)} T(v - \delta^{k,i}) \\
E_{k,k} T(v)
	&= (|v|_k - |v|_{k-1} + k -1) T(v)
\end{align*}


\item \label{GT-action} 
For each $1 \leq k \leq m \leq n$, we have $c_{m,k} T(v) 
= \gamma_{m,k}(v) T(v)$.

\item With this structure, $V(\lambda)$ is a finite dimensional representation
of maximal weight $\lambda$.
\end{enumerate}
\end{Theorem}

\paragraph
\label{GT-generic}
We will now reprove the following result due to Drozd, Futorny and Ovsienko.
\begin{Theorem*}[Futorny-Droz-Ovsyenko]
Let $w \in \CC^N$. If $w$ is generic then replacing $V(\lambda)$ with $V(w)$, 
items (\ref{GT-structure}) and (\ref{GT-action}) of \ref{GT} hold mutatis 
mutandis (in particular the condition on $v$ being standard is void).
\end{Theorem*}

We give a proof of this result. In order to do that we need a lemma.

\begin{Lemma*}
Let $W \subset \ZZ^N_0$ be a finite set and let $S_W = \bigcap_{w \in W} 
\CC^N_\std - w$. Let $F \in \CC(\lambda_{k,i} \mid 1 \leq i \leq k \leq n)$ be 
a rational function which is well defined in a set containing $S_W$. If $F(v) 
= 0$ for all $v \in S_W$, then $F = 0$.
\end{Lemma*}
\begin{proof}
Explicitly, $v$ lies in $S_W$ if and only if
\begin{align*}
v_{k,i} - v_{k-1,i} - \max_{w \in W}\{w_{k-1,i} - w_{k,i}, 0\} +1 
	&\in \ZZ_{> 0}, \\
v_{k-1,i} - v_{k,i+1} - \max_{w \in W}\{w_{k,i+1} - w_{k-1,i}\}.
	&\in \ZZ_{>0} 
\end{align*}
We enumerate the coordinate functions of a tableau as follows: start by 
$\lambda_{n,n}$, which we denote by $x_1$; then, looking at all entries with 
second coordinate $n-1$, we enumerate them by taking $x_2 = 
\lambda_{n-1,n-1}$, then $x_3 = \lambda_{n,n-1}$; next we take the elements 
with second coordinate $n-2$ starting by $\lambda_{n-2,n-2}$ and moving in the 
northwest direction. Explicitly, setting $\phi(i,j) = (i-j+1) + 
\frac{(n-j)(n-j+1)}{2}$ we write $x_{\phi(i,j)} = \lambda_{i,j}$. The 
following figure shows the enumeration corresponding to $n = 3$; two entries 
are joined by an edge if and only if they appear in one of the inequalities 
defining $S_W$, and in all cases the leftmost appears with a plus sing and the 
rightmost with a minus.

\begin{tikzpicture}
\node (31) at (0,3) {$\lambda_{3,1}$};
\node (32) at (2,3) {$\lambda_{3,2}$};
\node (33) at (4,3) {$\lambda_{3,3}$};
\node (21) at (1,2) {$\lambda_{2,1}$};
\node (22) at (3,2) {$\lambda_{2,2}$};
\node (11) at (2,1) {$\lambda_{1,1}$};

\node (31a) at (6,3) {$x_6$};
\node (32a) at (8,3) {$x_3$};
\node (33a) at (10,3) {$x_1$};
\node (21a) at (7,2) {$x_5$};
\node (22a) at (9,2) {$x_2$};
\node (11a) at (8,1) {$x_4$};

\draw (33) -- (22) -- (11)  (32) -- (21);
\draw (22) -- (32)  (11) -- (21) -- (31);

\draw (33a) -- (22a) -- (11a)  (32a) -- (21a);
\draw (22a) -- (32a)  (11a) -- (21a) -- (31a);
\end{tikzpicture}

With this enumeration, all the equations defining $S_W$ read as $x_r(v) - 
x_s(v) - t_{r,s} \in \ZZ_{>0}$ for some $t_{r,s} \in \ZZ$, and in each case 
$r > s$. Thus if we put $x_1(v) = 0$ then by induction for each $s = 1, 
\ldots, N$ there is always an $x_s(v)$ satisfying all equations involving 
$x_r$ with $r\leq s$. In this way we find a tableau in $S_W$, so in particular 
$S_W$ is not empty. 

For each $s \in [N]$, let $w_s \in \ZZ^N$ be the tableau such that $x_t(w_s) 
= 1$ if $t \geq s$, and $x_t(w_s) = 0$ if $t < s$. Notice that $v \in S_W$ 
implies $v + r w_s \in S_z$ for all $r \in \NN$. 
Let $f/g$ be the reduced expression of $F$. The hypothesis implies that if 
$v \in S_W$ then $f(v) = 0$ and $g(v) \neq 0$, and all we have to prove is 
that $f = 0$; we will do this by induction on the highest $t$ such that $x_t$ 
appears in $f$. If $f$ is a polynomial on $x_1$, then taking $v \in S_z$, our 
hypothesis implies that $f(v + rw_1) = 0$ for all $r \in \NN$, which can only 
happen if $f = 0$. Assuming the result holds for all numbers less than $t$, we 
write $f$ as a polynomial in $x_t$ with coefficients in the ring of polynomial 
functions on $x_1, \ldots, x_{t-1}$, so $f = f_0 + f_1 x_t + \cdots + f_l 
x_t^l$. Fix $v \in S_z$. For each $r \in \NN$ the value of $f_i(v + rw_t)$ is 
independent of $r$, since the entries below the $t$-th are fixed, so 
$f(v+rw_t)$ is a polynomial in $r$ whose $i$-th coefficient equals $f(v)$.
Since $f(v + rw_s) = 0$ for all $r \in \NN$, we see that $f_i(v) = 0$. Now $v$ 
was arbitrary, so each $f_i$ is zero over $S_W$, which implies that $f_i = 0$ 
for all $i$ by the inductive hypothesis.
\end{proof}

\paragraph
Consider the action of $\ZZ^N$ over $\CC^N$, given by $v^z = v+z$. This induces
an action on $\Lambda$, given by $(z \cdot f)(v) = f(v^z)$.
This action extends naturally to the fraction field $K = 
\operatorname{Frac}(\Lambda) = \CC(\lambda_{k,i} \mid 1 \leq i \leq k \leq 
n)$. 

For the rest of this section let $\H$ be the infinite hyperplane arrangement 
in $\CC^N$ consisting of all hyperplanes defined by the equations 
$\lambda_{k,i} - \lambda_{k,j} - r$ for all $1 \leq i < j \leq k \leq n$ and 
all $r \in \ZZ$, and let $A \subset K$ be the algebra of rational functions 
whose poles are contained in $\H$. Notice that $A$ is stable by the action of
$\ZZ^N$.


\begin{Proposition}
Let $V_A$ be the $A$-module with basis $\{T(z) \mid z \in \ZZ^n_0\}$, and let 
$V_K = K \ot_A V_A$. We see $V_A$ as $A$-submodule of $V_K$ in the obvious way.

\begin{enumerate}[(a)]
\item \label{generic-GT-structure}
The vector space $V_K$ can be endowed with the structure of a $U$-module 
with the action of the canonical generators given by
\begin{align*}
E_{k,k+1} T(z) 
	&= - \sum_{i=1}^k \frac{p^+_{k,i}(\lambda^z)}{q_{k,i}(\lambda^z)} 
		T(z + \delta^{k,i}); \\
E_{k+1,k} T(z) 
	&= \sum_{i=1}^k \frac{p^-_{k,i}(\lambda^z)}{q_{k,i}(\lambda^z)} 
		T(z - \delta^{k,i}); \\
E_{k,k} T(z)
	&= (|\lambda^z|_k - |\lambda^z|_{k-1} + k -1) T(z).
\end{align*}

\item For each $1 \leq k \leq m \leq n$, we have $c_{m,k} T(z) = 
\gamma_{m,k}(\lambda^z) T(z)$.

\item The $A$-module $V_A$ is a sub $U$-module of $V_K$.
\end{enumerate}
\end{Proposition}

\begin{proof}
Let $F$ be the free $\CC$-algebra generated by $X_{k,k+1}, X_{k+1,k}$ for 
$1 \leq k < n$, and $X_{k,k}$ for $1 \leq k \leq n$; there is an obvious map
$\phi: F \to U$. The formulas in item \ref{generic-GT-structure} define an 
$F$-module structure on $V_K$, so there is an algebra map $F \to \End_K V_K$, 
and we must show that this map factors through $U$.

Let $a \in F$ be a linear combination of monomials of length at most $r \geq 
0$. Then for each $w \in \ZZ^N_0$ there exists a rational function $f_a(-,w) 
\in K$ such that
\[
	aT(z) = \sum_{w \in \ZZ^N_0} f_a(\lambda^z,w) T(z+w)
\]
for all $z \in \ZZ^N_0$. Furthermore if the sum of the absolute values of the
entries of $w$ is greater than $r$ then $f_a(-,w) = 0$, so in fact the sum is 
over a finite set $W$. By Lemma \ref{GT-generic} the rational function 
$f_a(-,w)$ is determined by its values on $S_W = \bigcap_{w \in W} 
\CC_\std^N-w$.

Fix $v \in S_W$ and let $\lambda = (v_{n,1}, v_{n,1} + 1, \ldots, v_{n,n} + 
n -1)$. Since $v$ is standard $\lambda$ is a weight of $\gl(n,\CC)$, so we can
consider the representation $V(\lambda)$ as defined in \ref{GT}. By 
construction the set $\{T(v+w) \mid w \in W\} \subset V(\lambda)$ consists of 
nonzero linearly independent elements, and by construction
\[
	\phi(a) T(v) = \sum_{w \in W} f_a(v, w) T(v+w).
\]
Thus if $\phi(a) = 0$ then $f_a(v,z) = 0$ for all $v \in S_W$ and hence 
$f_a(-,w) = 0$, and the formulas in item \ref{generic-GT-structure} indeed 
define a $U$-module structure on $V_K$. Furthermore, if $\phi(a) = c_{m,k}$ for
some $k$ and $m$ then $f_a(v,z) = 0$ for all $z \neq 0$ and $f_a(v,0) = 
\gamma_{m,k}(v)$, and again by Lemma \ref{GT-generic} we get item (b). Item 
(c) follows from the definition.
\end{proof}

\paragraph
\label{GT-generic-proof}
\begin{proof}[Proof of Theorem \ref{GT-generic}]
If $w \in \CC_\gen^N$ then the map $f \in A \mapsto f(w) \in \CC$ is well
defined, and induces a one-dimensional representation of $A$ which we denote
$\CC_w$. Now $\CC_w \ot_A V_A$ is a $U$-module, with the action of $U$ induced
by its action on $V_A$, and furthermore it is isomorphic to $V(w)$ as 
$\CC$-vector space through the assignation $1 \ot_A T(z) \mapsto T(w+z)$. 
This provides the desired action of $U$ on $V(w)$.
\end{proof}

\section{$1$-singular GT-modules}
We extend the construction from Theorem \ref{GT-generic} to the case were
$w$ is $1$-critical.

\paragraph
Let $\Sigma = \{(k,i,j) \mid 1 \leq i < j \leq k \leq n\}$, and fix $(t,r,s) 
\in \Sigma$; write $x = \lambda_{t,r}, y = \lambda_{t,s}$. Let $B \subset A$ 
be the algebra of all rational functions in $A$ without poles in the hyperplane
$x-y$, i.e. $B$ consists of all functions in $A$ that can be evaluated in a 
$1$-critical tableau $v$ whose critical entries are precisely $x(v)$ and 
$y(v)$.

\paragraph
Let $\tau \in S_t$ be the permutation $(rs)$. We see $\tau $ as an element of
$G = S_1 \times S_2 \times \cdots \times S_n$ in the obvious way. This element
induces a linear transformation $\tau : \CC^N \to \CC^N$, which on the 
canonical basis is defined by 
\begin{align*}
\tau(\delta^{k,i})
	&= \begin{cases}
		\delta^{t,\tau(i)} & \mbox{ if } k = t; \\
		\delta^{k,i} & \mbox{ otherwise. }
	\end{cases}
\end{align*}
Clearly $\tau^2 = \Id$.

Recall that $K = \CC(\lambda_{k,i} \mid 1 \leq k \leq i \leq n)$ and that $V_K$
is the $K$-vector space with basis $\{T(z) \mid \ZZ^N_0\}$. For each $z \in 
\ZZ_0^N$ we define   
\begin{align*}
S(z) 
	&= \frac{T(z) + T(\tau(z))}{2},
&A(z)
	&= \frac{T(z) - T(\tau(z))}{2(x-y)}.
\end{align*}
Notice that $S(\tau(z)) = S(z)$ and $A(\tau(z)) = - A(z)$, so if $x(z) = y(v)$,
or equivalently $\tau(z) = z$, then $S(z) = T(z)$ and $A(z) = 0$. Also notice
that $T(z) = S(z) + (x-y)A(z)$, so the set $\{S(z), A(z) \mid z \in \ZZ_0^N\}$
generates $V_K$, and removing $0$ it is in fact a $K$-basis.

\paragraph
\label{GT-singular}
Our aim is to prove the following proposition.
\begin{Proposition*}
Let $V_B$ be the $B$-module generated by $\{S(z), A(z) \mid z \in \ZZ_0^N\}$.
Then $V_B \subset V_K$ is a sub-$U$-module.
\end{Proposition*}
Suppose the proposition is proved, and let $v \in \CC^N$ be a $1$-critical 
tableau with critical entries $v_{t,r}, v_{t,s}$. Then $v$ induces a 
$1$-dimensional representation of $B$ denoted by $\CC_v$, and we can recover
the $1$-critical module of \cite{FGR} taking $\CC_v \ot_B V_B$. In order to 
prove the proposition, we have to show that for all adequate $k$ the
$B$-module $V_B$ is stable by the action of $E_{k,k}, E_{k,k+1}$ and 
$E_{k+1,k}$. This is long and tedious, so we go step by step. We begin with
a lemma that gathers some properties of the relevant functions.

\begin{Lemma*}
\begin{enumerate}
\item \label{depends}
The polynomial $p_{k,i}^\pm$ depends only on $\lambda_{k,i}$ and 
$\lambda_{k \pm 1,j}$ with $1 \leq j \leq k \pm 1$. 
The polynomial $q_{k,i}$ depends only on $\lambda_{k,j}$ with $1 \leq j \leq 
k$.

\item \label{x-y-q}
We have $(x-y) \mid q_{k,i}(\lambda^z)$ if and only if $(k,i) \in 
\{(t,r), (t,s)\}$ and $z = \tau(z)$, and in that case $(x-y)^2$ does not
divide $q_{k,i}(\lambda^z)$.

\item \label{cosito}
For each $z \in \ZZ^N_0$ 
\[
F^\pm_z = \frac{p^\pm_{t,r}(\lambda^z)}{q_{k,r}(\lambda^z)} 
+ \frac{p^\pm_{t,s}(\lambda^{z})}{q_{k,s}(\lambda^{z})}\ \in B,
\]

\item \label{cosito2}
For each $z \in \ZZ^N_0$
\[
D_z^\pm =
\frac{1}{x-y}\left(\frac{p_{k,i}^\pm(\lambda^z)}{q_{k,i}(\lambda^z)} 
- \frac{p_{k,i}^\pm(\lambda^{\tau(z)})}{q_{k,i}(\lambda^{\tau(z)})}\right) 
\in B
\]
\end{enumerate}
\end{Lemma*}
\begin{proof}
The first two items are obvious by inspection, and the third follows from the 
second except if $\tau(z) = z$. Now $q_{t,r} = (x-y) \prod_{i \neq r,s}(x^z - 
\lambda_{t,i})$ and $q_{t,s} = (y-x) \prod_{i \neq r,s}(y^z - \lambda_{t,i})$.
Set
\[
G_z^\pm 
= \frac{p^\pm_{t,r}(\lambda^z)}{\prod_{i \neq r,s}(x^z - \lambda_{t,i}^z)} 
- \frac{p^\pm_{t,s}(\lambda^{z})}{\prod_{i \neq r,s}(y^z - \lambda_{t,i}^z)}
\]
Now $G_z^\pm \in B$ and $F_z = G_z/(x-y)$, so it is enough to show that 
$(x-y) \mid G_z^\pm$ in $B$, or in other words that the image of $G_z^\pm$ in 
the quotient ring $B/(x-y)$ is zero. Clearly the image of both denominators in 
the quotient is the same, and direct inspection shows that the same happens 
with the numerators. 

For the fourth item, notice that $z = \tau(z)$ implies $D_z = 0$, so we have 
$E_z^\pm = (x-y)D_z^\pm \in B$ for all $z$. Direct calculations show that
$E_z \equiv 0 \mod x-y$.
\end{proof}

\paragraph
\about{Action of $E_{k,k}$}

Since $|\lambda^z|_k = |\lambda^{\tau(z)}|_k = |\lambda|_k + |z|_k$
for all $k$, we obtain
\begin{align*}
E_{k,k} S(z) 
	&= (|\lambda^z|_k - |\lambda^z|_{k-1} + k -1) S(z) \\
E_{k,k} A(z) 
	&= (|\lambda^z|_k - |\lambda^z|_{k-1} + k -1) A(z)
\end{align*}
Thus $V_B$ is stable by the action of $E_{k,k}$.

\paragraph
\about{Action of $E_{k,k+1}$ on $S(z)$ for $k \neq t$}

The hypothesis that $k \neq t$ implies that $\tau(z) + \delta^{k,i} = 
\tau(z + \delta^{k,i})$ and also that $q_{k,i}(\lambda^z) = 
q_{k,i}(\lambda^{\tau(z)})$ for all $i$. Thus by definition
\begin{align*}
E_{k,k+1} S(z)
	&= - \frac{1}{2}
		 	\sum_{i=1}^k \frac{1}{q_{k,i}(\lambda^z)} 
			\left(
			p_{k,i}^+(\lambda^z) T(z+\delta^{k,i})
			+ p_{k,i}^+(\lambda^{\tau(z)}) T(\tau(z + \delta^{k,i}))
		\right) 
\end{align*}
By item \ref{x-y-q} of Lemma \ref{GT-singular} $1/q_{k,i}(\lambda^z) \in B$.
Since $T(z) = S(z) + (x-y)A(z) \in V_B$ the right hand side of the equation 
lies in $V_B$. 

Let us refine that result. If we assume that $k \neq t,t-1$ then 
$p_{k,i}(\lambda^z) = p_{k,i}(\lambda^{\tau(z)})$, so the previous formula 
becomes
\begin{align}
\label{k-k+1-S}
E_{k,k+1} S(z) 
	&= - \sum_{i = 1}^k \frac{p^+_{k,i}(\lambda^z)}{q_{k,i}(\lambda^z)}
	S(z+\delta^{k,i}).
\end{align}
If we take $k = t-1$ then we can replace $T(z)$ by $S(z) + (x-y)A(z)$ and
obtain
\begin{align}
\label{t-1-t-S}
E_{t-1,t} S(z)
	&= -\frac{1}{2}\sum_{i=1}^{t-1} \frac{p^+_{t-1,i}(\lambda^z) + 
	p^+_{t-1,i}(\lambda^{\tau(z)})}{q_{t-1,i}(\lambda^z)} 
	S(z + \delta^{t-1,i}) + \\
	&\qquad \quad + \frac{p^+_{t-1,i}(\lambda^z) - 
	p^+_{t-1,i}(\lambda^{\tau(z)})}{q_{t-1,i}(\lambda^z)} (x-y)
	A(z + \delta^{t-1,i}).
\end{align}

\paragraph
\about{Action of $E_{t,t+1}$ on $S(z)$}
Using the equality $T(z) = S(z) + (x-y)A(z)$, and the fact that $S(\tau(z) + 
\delta^{k,i}) = S(z+\tau(\delta^{k,i}))$ and $A(\tau(z) + \delta^{k,i}) = - 
A(z+\tau(\delta^{k,i}))$ we get
\begin{align*}
E_{t,t+1} S(z)
	&= -\frac12\sum_{i=1}^t \frac{p^+_{t,i}(\lambda^z)}{q_{k,i}(\lambda^z)}
		(S(z + \delta^{t,i}) + (x-y)A(z + \delta^{t,i})) + \\
		&\qquad \qquad 
		+ \frac{p^+_{t,i}(\lambda^{\tau(z)})}{q_{k,i}(\lambda^{\tau(z)})}
		\Big(S(z + \tau(\delta^{t,i})) - (x-y)A(z + \tau(\delta^{t,i}))\Big)
\end{align*}
By definition of $\tau$, we get
\begin{align}
E_{t,t+1}S(z)
	&=-\frac12\sum_{i = 1}^t 
	\left(\frac{p^+_{t,i}(\lambda^z)}{q_{t,i}(\lambda^z)} 
+ \frac{p^+_{t,\tau(i)}(\lambda^{\tau(z)})}{q_{t,\tau(i)}
(\lambda^{\tau(z)})}\right)S(z + \delta^{t,i}) + \\
& \qquad \qquad +
\left(\frac{p^+_{t,i}(\lambda^z)}{q_{t,i}(\lambda^z)} 
- \frac{p^+_{t,\tau(i)}(\lambda^{\tau(z)})}{q_{t,\tau(i)}
(\lambda^{\tau(z)})}\right)(x-y)A(z+\delta^{t,i}).
\end{align}
The coefficients of the $S$'s and the $A$'s' in this formula lie in $B$ unless
$z = \tau(z)$, in which case there might be problems when $i = r$ or $i = s$.
In that case the coefficient of the $A$'s lie in $B$ because $(x-y)$ divides 
$q_{t,r}$ and $q_{t,s}$ exactly once. Thus all we have to prove is that
if $z = \tau(z)$ then the coefficients of $S(z+\delta^{t,r})$ and 
$S(z+\delta^{t,s})$ lie in $B$ but this is precisely item \ref{cosito} of 
Lemma \ref{GT-singular}.

\paragraph
\about{Action of $E_{k+1,k}$ on $S(z)$}
Similar reasoning works for this case. We only state the results.
\begin{align*}
E_{k+1,k}S(z) 
	&= \sum_{i=1}^k \frac{p_{k,i}^-(\lambda^z)}{q_{k,i}(\lambda^z)}
	S(z - \delta^{k,i}) & (k \neq t,t+1)\\
E_{t+2,t+1}S(z)
	&= \frac12\sum_{i=1}^{t+1} 
	\frac{p^-_{t+1,i}(\lambda^z) + p^-_{t+1,i}(\lambda^{\tau(z)})}
	{q_{t+1,i}(\lambda^z)} S(z - \delta^{t+1,i}) + \\
	&\qquad \quad 
	+ \frac{p^-_{t+1,i}(\lambda^z) - p^-_{t+1,i}(\lambda^{\tau(z)})}
	{q_{t+1,i}(\lambda^z)} (x-y) A(z - \delta^{t+1,i}) \\
E_{t+1,t} S(z)
	&= \frac12 \sum_{i=1}^t \left(
	\frac{p^-_{t,i}(\lambda^z)}{q_{t,i}(\lambda^z)} 
	+ \frac{p^-_{t,\tau(i)}(\lambda^{\tau(z)})}
	{q_{t,\tau(i)}(\lambda^{\tau(z)})}\right) S(z - \delta^{t,i}) + \\
	& \qquad \qquad +
		\left(\frac{p^-_{t,i}(\lambda^z)}{q_{t,i}(\lambda^z)} - 
		\frac{p^-_{t,\tau(i)}(\lambda^{\tau(z)})}{q_{t,\tau(i)}
		(\lambda^{\tau(z)})}\right)(x-y)A(z - \delta^{t,i})
\end{align*}

\paragraph
\about{The action on $A(z)$}
Arguments similar to those above show that we get
\begin{align*}
E_{k,k+1} A(z) 
	&= - \sum_{i = 1}^k \frac{p^+_{k,i}(\lambda^z)}{q_{k,i}(\lambda^z)}
	A(z) & (k \neq t,t-1)\\
E_{t-1,t} A(z)
	&= -\frac12 \sum_{i=1}^{t-1} 
	\frac{p_{t-1,i}^+(\lambda^z) - p_{t-1,i}^+(\lambda^{\tau(z)})}
	{(x-y)q_{t-1,i}(\lambda^z)} S(z + \delta^{t-1,i}) \\
	&\qquad \qquad + \frac{p_{t-1,i}^+(\lambda^z) + p_{t-1,i}^+(\lambda^{\tau(z)})}
	{q_{t-1,i}(\lambda^z)}A(z + \delta^{t-1,i}) \\
E_{t,t+1} A(z)
	&= -\frac12 \sum_{i=1}^t \frac{1}{x-y}\left( 
		\frac{p_{t,i}^+(\lambda^z)}{q_{t,i}(\lambda^z)} - 
		\frac{p_{\tau(t,i)}^+(\lambda^{\tau(z)})}{q_{\tau(t,i)}(\lambda^{\tau(z)})}\right) 
		S(z + \delta^{t,i}) \\
	& \qquad \qquad 
	+ \left(\frac{p_{t,i}^+(\lambda^z)}{q_{t,i}(\lambda^z)} 
	+ \frac{p_{\tau(t,i)}^+(\lambda^{\tau(z)})}{q_{\tau(t,i)}(\lambda^{\tau(z)})}\right) 
	A(z + \delta^{t,i}).
\end{align*}

Similarly we get
\begin{align*}
E_{k+1,k} A(z) 
	&= \sum_{i=1}^k \frac{p_{k,i}^-(\lambda^{z})}{q_{k,i}(\lambda^{z})}
	A(z - \delta^{k,i}) & (k \neq t,t+1) \\
E_{t+2,t+1} A(z)
	&= \frac12 \sum_{i=1}^{t+1} \frac{p_{t+1,i}^-(\lambda^z) - 
	p_{t+1,i}^-(\lambda^{\tau(z)})}
	{(x-y)q_{t+1,i}(\lambda^z)}S(z - \delta^{t+1,i}) \\
	&\qquad \qquad + \frac{p_{t+1,i}^-(\lambda^z) + 
	p_{t+1,i}^-(\lambda^{\tau(z)})}
	{q_{t+1,i}(\lambda^z)}A(z-\delta^{t+1,i}) \\
E_{t,t+1} A(z)
	&= -\frac12 \sum_{i=1}^t \frac{1}{x-y}\left( 
		\frac{p_{t,i}^-(\lambda^z)}{q_{t,i}(\lambda^z)} - 
		\frac{p_{t,\tau(i)}^-(\lambda^{\tau(z)})}{q_{t,\tau(i)}(\lambda^{\tau(z)})}\right) 
		S(z - \delta^{t,i}) \\
	& \qquad \qquad 
	+ \left(\frac{p_{t,i}^-(\lambda^z)}{q_{t,i}(\lambda^z)} 
	+ \frac{p_{t,\tau(i)}^-(\lambda^{\tau(z)})}{q_{t,\tau(i)}(\lambda^{\tau(z)})}\right) 
	A(z - \delta^{k,i}).
\end{align*}

\paragraph
\about{The action of $\Gamma$ on $S(z), A(z)$}
By carrying things out as before we get
\begin{align*}
c_{m,k} S(z)
	&= \gamma_{m,k}(\lambda^z)S(z) 
&c_{m,k} A(z)
	&= \gamma_{m,k}(\lambda^z)A(z) 
	&(m \neq t),
\end{align*}
while for $k = t$
\begin{align*}
c_{t,k} S(z)
	&= \frac{\gamma_{m,k}(\lambda^z) + \gamma_{m,k}(\lambda^{\tau(z)})}{2} S(z)
		+ (x-y)\frac{\gamma_{m,k}(\lambda^z) - \gamma_{m,k}(\lambda^{\tau(z)})}
		{2}A(z) \\
c_{t,k} A(z)
	&= \frac{\gamma_{m,k}(\lambda^z) + \gamma_{m,k}(\lambda^{\tau(z)})}{2}A(z)
		+ \frac{\gamma_{m,k}(\lambda^z) - \gamma_{m,k}(\lambda^{\tau(z)})}
		{2(x-y)}S(z)
\end{align*}
Notice that this makes it less obvious whether $V_B$ is a GT-module.

\paragraph
\about{The generic $1$-singular $U$-module}
Set $B' = B/(x-y)$, and $V' = B' \ot_B V_B$. Clearly for any $w \in \CC^N$ 
with $x(w) = y(w)$ the $B$-module $\CC_w$ is also a $B'$-module. Thus to study 
the generic $U$-module over a $1$-critical tableau we look at the action of
$U$ on $V'$.

\begin{align*}
E_{k,k+1} S(z)
	&\equiv -\sum_{i=1}^k \frac{p_{k,i}^+(\lambda^z)}{q_{k,i}(\lambda^z)} 
	S(z+\delta^{k,i}) \mod (x-y) &(z \neq \tau(z) \mbox{ 0 } k \neq t); \\
E_{t,t+1} S(z)
	&\equiv -\sum_{i=1}^t \frac{p_{t,i}^+(\lambda^z)}{q_{t,i}(\lambda^z)} 
	S(z+\delta^{t,i}) \\&\qquad \qquad + 2\frac{p^+_{t,r}(\lambda^z)}{\hat q_{t,r}(\lambda^z)} A(z+\delta^{t,r}) \mod (x-y) &(z = \tau(z)) \\
E_{k+1,k} S(z)
	&\equiv \sum_{i=1}^k \frac{p_{k,i}^-(\lambda^z)}{q_{k,i}(\lambda^z)} 
	S(z-\delta^{k,i}) \mod (x-y) &(z \neq \tau(z) \mbox{ 0 } k \neq t); \\
E_{t,t+1} S(z)
	&\equiv \sum_{i=1}^t \frac{p_{t,i}^-(\lambda^z)}{q_{t,i}(\lambda^z)} 
	S(z-\delta^{t,i}) \\&\qquad \qquad + 2\frac{p^-_{t,r}(\lambda^z)}{\hat q_{t,r}(\lambda^z)} A(z-\delta^{t,r}) \mod (x-y) &(z = \tau(z))
\end{align*}
where $\hat q_{t,r} = q_{t,r}/(x-y)$.
\begin{align*}
E_{k,k+1} A(z)
	&\equiv -\sum_{j=1}^k \frac{p_{k,i}^+(\lambda^z)}{q_{k,i}(\lambda^z)}
	A(z+\delta^{k,i}) \mod (x-y)&(k \neq t,t-1) \\
E_{t-1,t} A(z) 
	&\equiv -\sum_{j=1}^{t-1} \frac{p_{t-1,i}^+(\lambda^z)}
	{q_{t-1,i}(\lambda^z)} A(z+\delta^{t-1,i}) \\
	&\qquad \qquad + \frac{(b-a)}{2}\frac{\hat p^+_{t-1,i}(\lambda^z)}
	{q_{t-1,i}(\lambda^z)} S(z + \delta^{t-1,i})\\
E_{t,t+1} A(z)
	&\equiv -\sum_{j=1}^{t} \frac{p_{t,i}^+(\lambda^z)}
	{q_{t,i}(\lambda^z)} A(z+\delta^{t,i}) \\
	&\qquad \qquad + \frac{a-b}{2} \frac{p_{t,i}^+(\lambda^z)}
	{mcm(q_{t,i}(\lambda^z),q_{t,i}(\lambda^{\tau(z)}))} S(z + \delta^{t,i})
\end{align*}
where $\displaystyle \hat p_{t \mp 1,i}^\pm = \prod_{j \neq r,s}^{t\mp 1} 
(\lambda_{t\mp 1, i} - \lambda_{t,j})$.


\newpage

\section{The search for the general formula}

I want to find out how to construct a module associated with a $2$-critical
tableau. I work with tableaux of heigth $4$, and write $x = \lambda_{3,1}, y 
= \lambda_{3,2}, z = \lambda_{3,3}$. I will deal with the case $x = y = z$.

The idea is the following. Let $B = \{f/g \in A \mid g \mbox{ is not divisible 
by any of } (x-y), (x-z), (y-z)\}$, so a $2$-critical tableau $v$ with $x(v) = 
y(v) = z(v)$ still defines a $1$-dimensional $B$-module $\CC_v$. We wish to 
find a $B$-lattice $V_B \subset V_K$ which is stable by the action of 
$\gl(4,\CC)$, so $\CC_v \ot_B V_B$ defines a module associated to the tableau.

\paragraph
If $v \in \CC^6$ I will write $T(x(v), y(v), z(v))$ for $T(v)$.

\paragraph
The group $S_3$ acts naturally on $\ZZ^3$, so it acts on the third row of 
tableaux and induces an action of $S_3$ over $V_K$, for example $(123) 
T(a,b,c) = T(c,a,b)$ (yes, that is the right one, I checked. Go ahead, check 
again). Since $S_3$ is just one of the many symmetric groups acting, let us
write 
\begin{align*}
\sigma(k,i)
	&\begin{cases}
		(k,i) & k \neq 3 \\
		(3,\sigma(i)) & k = 3.
	\end{cases}
\end{align*}

The orbit of $T(a,b,c)$ by this action is generated by the following vectors
\begin{align*}
\Sym(a,b,c) 
	&= \sum_{\sigma \in S_3} \sigma T(a,b,c) \\
\Alt(a,b,c) 
	&= \sum_{\sigma \in S_3} \sg(\sigma) \sigma T(a,b,c) \\
v_1(a,b,c) 
	&= \sum_{i = 0}^2 \omega^i (123)^iT(a,b,c) &
v_2(a,b,c) 
	&= \sum_{i = 0}^2 \omega^i (12)(123)^iT(a,b,c) \\
w_1(a,b,c) 
	&= \sum_{i = 0}^2 \overline \omega^i (123)^iT(a,b,c) &
w_2(a,b,c) 
	&= \sum_{i = 0}^2 \overline \omega^i (12)(123)^iT(a,b,c) \\
\end{align*}
with $\omega$ a cubic root of unity. Vectors on the same line generate a
stable subspace.

\paragraph
The action of $S_3$ induces an action on $K$, with $(\sigma \cdot p)
(x,y,z)= p(\sigma^{-1}(x,y,z))$. Thus
\begin{align*}
 \sigma \cdot p^\pm_{3,j}
	& = p^\pm_{3,\sigma(j)}
	& \sigma \cdot p^\pm_{k,j} 
	& = p^\pm_{k,j} \ \ (k \neq 3) \\
\sigma \cdot q_{3,j} 
	& = q_{3,\sigma(j)} 
	& \sigma \cdot q_{k,j} 
	& = q_{k,j} \ \ (k \neq 3)
\end{align*}
Also $\sigma \cdot p(\lambda^{v}) = (\sigma \cdot p)(\lambda^{\sigma(v)})$.
Using our previous notation we get $\sigma \cdot p^{\pm}_{k,i} = 
p_{\sigma(k,i)}$ and $\sigma \cdot q_{k,i} = q_{\sigma(k,i)}$.

From this it follows that
\begin{align*}
E_{k,k+1} T(\sigma (v))
	&= \sum_{i=1}^k 
		\frac{p_{k,i}^+(\lambda^{\sigma(v)})}{q_{k,i}(\lambda^{\sigma(v)})}
		T(\sigma(v)+\delta^{k,i})\\
	&= \sum_{j=1}^k 
		\frac{p_{\sigma(k,j)}^+(\lambda^{\sigma(v)})}{q_{\sigma(k,j)}
		(\lambda^{\sigma(v)})} T(\sigma(v+\delta^{k,j})) \\
	&= \sum_{j=1}^k 
		\left(\sigma \cdot 
			\frac{p_{k,j}^+(\lambda^{v})}{q_{k,j}(\lambda^{v})} 
		\right) T(\sigma(v + \delta^{k,j})) \\
	&= \sigma\left(E_{k,k+1}T(v)\right)
\end{align*}

\paragraph
We put a scalar product over $V_K$, with $T(v)$ being an orthonormal basis.
Clearly $S_3$ acts by unitary operators


IDEA: Take $V_\CC$ as the $\CC$-space generated by the tableaux $\ZZ_0^N$, and 
let $S_k$ act on it. Now $S_k$ also acts on $K = \CC(\lambda)$, and hence on 
$V_K = K \ot_\CC V_\CC$, and the $E_{j,j+1}$ are compatible with the 
$S_n$-action. Let $\Delta = \prod_i(x_{k,i} - x_{k,j})$ and let $c_\lambda$ 
be the Schur projectors. I claim that
\begin{align*}
B c_1(V_\CC) 
	\oplus 
		\bigoplus_{\lambda \vdash n}\frac{1}{\Delta} \cdot Bc_\lambda(V_\CC)
\end{align*}
is $\gl(n,\CC)$-stable. Maybe changing $\Delta$ for $\Delta_\lambda$?


\newpage

\section{}

\paragraph
Fix $l < n$. The group $S_l$ acts on $\ZZ_0^N$, by permuting the entries in
the $l$-th row of the tableaux. It also acts on $K = \CC(\lambda)$ by 
permuting the generators $\lambda_{l,i}$ and fixing the others. With this
definition the algebra 
\[
B 
	= \{f/g \in A \mid \mbox{ $g$ is not divisible by }
		\lambda_{l,i} - \lambda_{l,j} \mbox{ for any } 1 \leq i < j \leq l\}
\]
is $S_l$-invariant.

Given $\sigma \in S_l$ we set 
\begin{align*}
\sigma(k,i)
	&= \begin{cases}
		(k,i) & k \neq l \\
		(l,\sigma(i)) & k = l.
	\end{cases}
\end{align*}
Thus $\sigma(\lambda_{k,j}) = \lambda_{\sigma(k,j)}$. Also we get that
$\sigma \cdot p(v) = p(\sigma^{-1}(v))$ for each $\sigma \in S_l, p \in K$ and 
$v \in \ZZ_0^N$ whenever this makes sense.

\begin{Lemma*}
For each $1 \leq k \leq j \leq n$ and each $\sigma \in S_l$ the following 
formulas hold.
\begin{align*}
\sigma \cdot p_{k,j}^\pm 
	&= p_{\sigma(k,j)} 
	&\sigma \cdot q_{k,j} = q_{\sigma(k,j)}.
\end{align*}
Also $\sigma \cdot (p(\lambda^v)) = (\sigma \cdot p)(\lambda^{\sigma(v)})$
for each $v \in \CC^N$.
\end{Lemma*}

\begin{Proposition}
The operators $E_{k,k+1}, E_{k,k}, E_{k+1,k}$ are $S_l$-equivariant.
\end{Proposition}
\begin{proof}
Fix $\sigma \in S_l$. We have
\begin{align*}
E_{k,k+1}(\sigma\cdot T(v))
	&= -\sum_{j=1}^k 
		\frac{p_{k,j}^+(\lambda^{\sigma(v)})}{q_{k,j}(\lambda^{\sigma(v)})}
			T(\sigma(v) + \delta^{k,j}).
\end{align*}
Taking $(k,i) = \sigma^{-1}(k,j)$ the last sum equals
\begin{align*}
-\sum_{i=1}^k 
	\frac{p_{\sigma(k,i)}^+(\lambda^{\sigma(v)})}{q_{\sigma(k,i)}
		(\lambda^{\sigma(v)})}	T(\sigma(v + \delta^{k,i}))
	&= -\sum_{i=1}^k \sigma \cdot \left( 
		\frac{p_{k,i}^+(\lambda^{v})}{q_{k,i}(\lambda^{v})} T(v+\delta^{k,i})
		\right) = \sigma (E_{k,k+1} T(v)).
\end{align*}
The proofs that $E_{k+1,k}$ is equivariant is similar. In the case of $E_{k,k}$
the result follows immediately from the definitions.s
\end{proof}

\paragraph
We take the notation from \cite{FH-rt-book}*{chapter 4}. For each 
partition $\lambda \vdash l$ we set $e_\lambda$ to be the corresponding 
normalized Young symmetrizer, i.e. $e_\lambda^2 = e_\lambda$. We claim that
For each partition $\lambda$ there exists $\Delta_{\lambda} \in 
\CC[\lambda_{k,i}]$ such that 
\begin{align*}
V_B 
	&= \bigoplus_{\lambda \vdash l} \frac{1}{\Delta_\lambda} 
		B \ot_\CC e_\lambda(V_\CC)
\end{align*}
is a sub $U$-module of $V_K$. My not-so-educated guess at this point is the
following: write $E_{l,l+1}T(0) = \sum_{\lambda \vdash l} \sum_i 
a_{\lambda, i}c_{\lambda}(T(\delta^{l,i}))$, and take $\Delta_\lambda$
such that $\Delta_\lambda a_{\lambda,i} \in B$. for all $i$.

\paragraph
A typical element of $V_B$ is of the form $\frac{f}{\Delta_\lambda} 
e_\lambda(T(v))$ with $v \in \ZZ^N_0$, with $f \in B$. Thus we must prove
that $E_{k,k+1}(\frac{1}{\Delta_\lambda} e_\lambda(T(v))) \in V_B$. 

\paragraph
We associate to each $v \in \ZZ^l$ a partition of $l$ as follows. 
Let us call $a$ the most common value in $v$, and set $\lambda_1$ as the 
number of entries equal to $a$; calling $b$ the second most repeated value 
then $\lambda_2$ is the number of entries equal to $b$, etc. For example, if 
$l = 14$ and $v = (a,a,a,a,a,b,b,b,b,c,c,d,e,f)$ then $\lambda = 
(5,4,2,1,1,1)$. We write $\lambda(v)$ for the partition associated to $v$.
We say that $v$ is well-presented if all entries from $1$ to $\lambda_1$ are
equal, and the same holds for all entries from $\lambda_1 + 1$ to $\lambda_1 +
\lambda_2$, etc. Our example is well presented, and the same holds if we switch
the last two entries, but not if we exchange the first and the last, or if
we put the four $b$'s before the five $a$'s. Notice that the partition 
associated to $v$ is an $S_l$-equivariant function, and in particular for each 
$v$ there exists $\sigma \in S_l$ such that $\sigma(v)$ is well presented.

Now let $v \in \ZZ^N_0$. We denote by $\lambda_l(v)$ the partition associated 
to the $l$-th row of $v$.

\begin{Proposition*}
If $\mu < \lambda_l(v)$ then $c_\mu(T(v)) = 0$.
\end{Proposition*}
\begin{proof}
Let $V(v) = \CC[S_n] \cdot T(v)$. Since $c_\mu(T(v)) \in c_\mu(V(v))$
\end{proof}


\newpage
\begin{bibdiv}
\begin{biblist}
\bib{FGR}{article}{
   author={Futorny, Vyacheslav},
   author={Grantcharov, Dimitar},
   author={Ramirez, Luis Enrique},
   title={Singular Gelfand-Tsetlin modules of ${\germ{gl}}(n)$},
   journal={Adv. Math.},
   volume={290},
   date={2016},
   pages={453--482},
}

\bib{FH-rt-book}{book}{
   author={Fulton, William},
   author={Harris, Joe},
   title={Representation theory},
   series={Graduate Texts in Mathematics},
   volume={129},
   note={A first course;
   Readings in Mathematics},
   publisher={Springer-Verlag, New York},
   date={1991},
   pages={xvi+551}
}

\end{biblist}
\end{bibdiv}
\end{document}